%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Platform for sharing web dev projects} % Description
    {Showcase} % Project Title
    {
      % \href{https://tutoro-uw.herokuapp.com}{Live Site} | 
      \href{https://github.com/bernardjkim/showcase}{Github}
    } % Links
    {Jan. 2019 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Broke down application into separate services.}
        \item {Integrated Elasticsearch for a better search performance.}
        \item {Enabled communication between services with pub/sub messaging through RabbitMQ.}
        \item {Deployed application on a Kubernetes cluster hosted on DigitalOcean.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Discord clone, messaging web application} % Description
    {LOL Chat} % Project Title
    {
      % \href{https://lol-chatt.herokuapp.com}{Live Site} | 
      \href{https://github.com/bernardjkim/lol-chat}{Github}
    } % Links
    {Nov. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a simple chat server using Node and Socket.io for realtime communication.}
        \item {Implemented voice chat using WebRTC allowing P2P audio communication.}
        \item {Deployed a coTURN docker container to relay WebRTC media traffic.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web application for trading stocks with a mock portfolio} % Description
    {PTrade} % Project Title
    {
      % \href{https://p-trade.herokuapp.com}{Live Site} | 
      \href{https://github.com/bernardjkim/ptrade}{Github}
    } % Links
    {Jul. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a RESTful API in Go to handle user transactions stored in a MySQL database.}
        \item {Created scheduled tasks to pull the latest stock market prices from IEX's public API and log user data.}
        \item {Font-end built using React and tested using Jest}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Distributed key value store} % Description
    {KV Store} % Project Title
    {} % Location
    {Mar. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built a highly available, scalable, fault tolerant key-value store using Java.}
        \item{Implemented at-most-once RPC semantics to prevent duplication.}
        \item{Implemented the multi-Paxos algorithm for state machine replication.}
        \item{Partitioned the key set to improve system throughput.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Compiles MiniJava code into x86-64 assembly code} % Description
%     {MiniJava Compiler} % Project Title
%     {} % Location
%     {Mar. 2018 - Jun. 2018} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Worked in a team of two to build a \href{http://www.cambridge.org/resources/052182060X/} {\color{awesome-skyblue}MiniJava} compiler using Java. }
%         \item {Implemented the scanning and parsing phase utilizing JFlex/CUP java packages.}
%         \item {Implemented semantic checking and code generation using ASTs.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {UNIX-like operating system built on top of \href{https://pdos.csail.mit.edu/6.828/2012/xv6.html}{\color{awesome-skyblue}{xv6}}.} % Description
    {XK Operating System} % Project Title
    {} % Location
    {Sep. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Implemented I/O system calls (open/close/read/write/...).}
        \item{Enabled the operating system to run multiple processes with fork/exec.}
        \item{Added a relatively full-featured virtual memory system (LRU swapping, mmap, copy-on-write).}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}