\cvsection{PROJECTS}
\begin{cvskills}
    \cvproject
        {PTrade}
        {July 2018 - PRESENT}
        {\begin{cvitems} % Description(s) bullet points
            \item{Developed a REST API in \cvtag{Golang} to handle user transactions stored in a \cvtag{MySQL} database.}
            \item{Created scheduled tasks to pull the latest stock market prices and log user data for analytics.}
            \item{Font-end built using \cvtag{React.js} and \cvtag{Material-UI} for a responsive, minimalist UI.}
            \item{\href{https://p-trade.herokuapp.com}{Link: \color{blue}https://p-trade.herokuapp.com}.}
        \end{cvitems}}
\end{cvskills}

\begin{cvskills}
    \cvproject
        {KV Store}
        {Mar 2018 - Jun 2018}
        {\begin{cvitems} % Description(s) bullet points
            \item{Built a highly available, scalable, fault tolerant key-value store using \cvtag{Java.}}
            \item{Implemented at-most-once RPC semantics to prevent duplication.}
            \item{Utilized the multi-Paxos algorithm for state machine replication.}
            \item{Partitioned the key set to improve system throughput.}
        \end{cvitems}}
\end{cvskills}

\begin{cvskills}
    \cvproject
        {MiniJava Compiler}
        {Mar 2018 - Jun 2018}
        {\begin{cvitems} % Description(s) bullet points
            \item{
                Worked in a team of two to build a \href{http://www.cambridge.org/resources/052182060X/}
                {\color{blue}MiniJava} compiler using \cvtag{Java.}
            }
            \item{Implemented the scanning and parsing phase utilizing the JFlex/CUP tools.}
            \item{Implemented semantic checking and code generation using ASTs.}
        \end{cvitems}}
\end{cvskills}

\begin{cvskills}
    \cvproject
        {xk Operating System}
        {Sep 2017 - Dec 2017}
        {\begin{cvitems} % Description(s) bullet points
            \item{Built a UNIX-like operating system in \cvtag{C} from the base code of \href{https://pdos.csail.mit.edu/6.828/2012/xv6.html}{\color{blue}{xv6}}.}
            \item{Implemented a handful of system calls.}
            \item{Enabled the operating system to run multiple processes.}
            \item{Added a relatively full-featured virtual memory system (LRU swapping, mmap, copy-on-write).}
        \end{cvitems}}
\end{cvskills}